\section{\bench{}}

\bench{} evaluates deletion audits in three tracks. The RAG track deletes source documents, chunks, embeddings, caches, and summaries. The fine-tuning track deletes instruction records or preference examples that may have influenced an adapter. The hybrid track starts with RAG documents, generates synthetic instruction examples from them, fine-tunes an adapter, and then tests whether deleting the original source removes downstream behavior.

Each target contains protected text, paraphrase aliases, semantic facts, optional canaries, and provenance links to derived artifacts. Each audit method is evaluated on failure detection, false alarms, risk score, residual-dependence channels, retain utility, and audit calls.

The benchmark includes weak audit baselines: exact-match checks, canary-only checks, retriever-hit checks, uniform probes, and an \method{} ablation without valuation-guided prioritization. These baselines are deliberately included because they correspond to common but incomplete deletion-verification practices.

The extended benchmark also includes membership-inference, extraction-audit, and influence-proxy baselines. Membership inference scores direct and paraphrased answer dependence. Extraction auditing emphasizes adversarial extraction probes. The influence proxy aggregates direct, paraphrase, retrieval, and counterfactual channels as a lightweight approximation to expensive instance-influence methods.

To make the benchmark reusable, each run exports row-level JSON and CSV with seed, target size, audit budget, audit method, deletion method, decision, risk score, channel scores, retain utility, and call count. The benchmark card documents tracks, metrics, and release assumptions. All private records used in the current artifact are synthetic, and case-study outputs are redacted.
