\section{\bench{}}

\bench{} evaluates deletion audits in three tracks. The RAG track deletes source documents, chunks, embeddings, caches, and summaries. The fine-tuning track deletes instruction records or preference examples that may have influenced an adapter. The hybrid track starts with RAG documents, generates synthetic instruction examples from them, fine-tunes an adapter, and then tests whether deleting the original source removes downstream behavior. Each track now has three system states: $S_0$ before deletion, $S_-$ after the claimed deletion operation, and $S_{\mathrm{clean}}$ rebuilt or simulated as if the deletion target had never entered the pipeline.

Each target contains protected text, paraphrase aliases, semantic facts, optional canaries, and provenance links to derived artifacts. Each audit method is evaluated on counterfactual distinguishability from $S_{\mathrm{clean}}$, failure detection, false alarms, risk score, residual-dependence channels, retain utility, and audit calls.

The benchmark includes weak audit baselines that mirror common but incomplete practices--exact-match, canary-only, and retriever-hit checks, uniform probes, and an \method{} ablation without graph-adaptive allocation--alongside membership-inference (direct and paraphrased answer dependence), extraction-audit (adversarial extraction probes), influence-proxy (a lightweight aggregate of the direct, paraphrase, and retrieval channels), and a two-sample clean-counterfactual baseline that queries $S_-$ and $S_{\mathrm{clean}}$ on the same probes.

For causal localization, \bench{} includes intervention variants that disable retrieval, purge caches, replace adapters, or remove derivative stores while holding probes fixed. The reported mediation scores decompose residual risk into retrieval-mediated, cache-mediated, derivative-mediated, and parametric components when the intervention assumptions in Section~5 hold.

To make the benchmark reusable, each run exports row-level JSON and CSV with seed, target size, audit budget, audit method, deletion method, decision, counterfactual distance, risk score, channel scores, intervention scores, retain utility, and call count. The benchmark card documents tracks, metrics, clean-reference construction, adversary class, probe coverage assumptions, and release assumptions. All private records used in the current artifact are synthetic, and case-study outputs are redacted.
