% PROXY build for page-count verification ONLY (IEEEtran unavailable in sandbox).
% Geometry is slightly LOOSER than IEEEtran compsoc, so a <=10pp result here
% is a conservative guarantee that the real IEEEtran build is also <=10pp.
\documentclass[10pt,twocolumn]{article}
\usepackage[letterpaper,top=0.8in,bottom=0.95in,left=0.75in,right=0.75in,columnsep=0.25in]{geometry}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage{amsthm}

\newtheorem{proposition}{Proposition}
\newcommand{\method}{ADCU}
\newcommand{\bench}{ADCU-Bench}

% --- IEEEtran shims so the real sources/bbl compile under article ---
\newenvironment{IEEEkeywords}{\par\smallskip\noindent\textbf{Index Terms---}}{\par}
\providecommand{\BIBdecl}{}
\providecommand{\BIBentryALTinterwordspacing}{}
\providecommand{\BIBentryALTinterwordstretchfactor}[1]{}
\providecommand{\BIBentrySTDinterwordspacing}{}
\providecommand{\BIBforeignlanguage}[2]{#2}
\providecommand{\bibinfo}[2]{#2}

% --- minimal algorithm/algorithmic shims (packages absent in sandbox) ---
\newcounter{algctr}
\newenvironment{algorithm}[1][]{\par\addvspace{\medskipamount}\noindent\begin{minipage}{\columnwidth}\hrule\smallskip\refstepcounter{algctr}\def\caption##1{{\noindent\textbf{Algorithm \thealgctr:}~##1\par\smallskip\hrule\smallskip}}}{\smallskip\hrule\end{minipage}\par\addvspace{\medskipamount}}
\newcounter{ALnum}
\newenvironment{algorithmic}[1][0]{\footnotesize\begin{list}{\arabic{ALnum}:}{\usecounter{ALnum}\setlength{\leftmargin}{1.5em}\setlength{\itemsep}{0pt}\setlength{\parsep}{0pt}\setlength{\topsep}{2pt}}}{\end{list}}
\newcommand{\STATE}{\item}
\newcommand{\WHILE}[1]{\item \textbf{while} #1 \textbf{do}}
\newcommand{\ENDWHILE}{\item \textbf{end while}}
\newcommand{\IF}[1]{\item \textbf{if} #1 \textbf{then}}
\newcommand{\ELSIF}[1]{\item \textbf{else if} #1 \textbf{then}}
\newcommand{\ELSE}{\item \textbf{else}}
\newcommand{\ENDIF}{\item \textbf{end if}}

\title{\vspace{-2em}Auditable Unlearning for Retrieval-Augmented and Fine-Tuned Foundation Models}
\author{Author Names Omitted for Review}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Deletion requests in foundation-model applications are difficult to audit because user data can survive through retrievers, vector indexes, summaries, adapters, caches, and generated traces. This paper proposes \method{}, an auditable unlearning framework grounded in counterfactual behavioral indistinguishability: a post-deletion system should behave like a clean reference system rebuilt as if the deleted record had never entered the pipeline. \method{} lifts $(\varepsilon,\delta)$ deletion from model-centric removal to compositional RAG and fine-tuned AI systems, implements a graph-adaptive black-box test over provenance-linked target--channel arms, and uses diagnostic channels to localize residual risk under declared probe-coverage assumptions. \bench{} evaluates RAG deletion, fine-tuning record unlearning, hybrid RAG-to-fine-tuning retention, clean-counterfactual testing, and component interventions. Across 6,840 repeated audit rows, \method{} detects all configured RealRAG, NaturalFEVER, and HybridReal failures with zero configured false alarms; a 5,000-record RealRAG scaling check shows the behavior is not limited to tiny retain corpora. LoRA, dense-retrieval, TOFU-style, natural-data, and attack-suite experiments further show that narrow exact-match, canary-only, retriever-only, membership-style, and extraction-only audits miss important residual-dependence channels.
\end{abstract}

\noindent\textbf{Impact Statement---}
Foundation-model systems are increasingly used in settings where users, organizations, and regulators may require deletion of contributed data. Yet deletion claims are hard to trust when a record can survive through retrieval indexes, summaries, caches, adapters, or derivatives. This work advances trustworthy AI by turning deletion verification into a measurable behavioral audit for RAG and fine-tuned foundation models. The proposed metric, algorithm, benchmark, and attack suite help practitioners identify residual dependence, compare unlearning procedures, preserve retain utility, and document uncertainty through confidence-bounded decisions. The broader impact is a practical assurance layer for AI governance: rather than relying on informal claims that a model or pipeline has forgotten, operators can produce repeatable, redacted, and technically interpretable evidence about what was tested and where residual deletion risk remains.

\begin{IEEEkeywords}
Trustworthy artificial intelligence, machine unlearning, retrieval-augmented generation, foundation models, data provenance, behavioral auditing.
\end{IEEEkeywords}

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_problem}
\input{sections/04_metric}
\input{sections/05_algorithm}
\input{sections/06_benchmark}
\input{sections/07_experiments}
\input{sections/08_discussion}
\input{sections/09_artifact}
\input{sections/10_conclusion}

\input{/sessions/zealous-determined-knuth/mnt/outputs/refs.bbl}

\end{document}
